Home

### 2018-01-27 analysis/index.Rmd
Files commited by wflow_commit.
Updated NOTES.txt.

### simulation studies

@@

Click on this [Questions on Algorithm](first-analysis.html) to see more details.

### flash on the chipseq data from Kevin

Click on this [three data sets on the 4500 rows chr1 var_col](sd_chr1_asinh.html) to see more details.

[ns](draft.html)

Click on this [load reslut of GTEx data](GTExresult.html) to see more details.

Click on this [pairwise plot](pairwiseplotofflashgtexzscore.html) to see more details.

### Issues

Click on this [gap issue](ObjGap.html) to see more details. (test)

Click on this [summary of the rank0 vs rank1](Obj_summary.html) to see a simple summary to the following two items.

- Click on this [rank 0 vs rank 1](Objcheck_1.html) to see more details.
- Click on this [rank 0 vs rank 1: fdr with penalty](Objcheck_2.html) to see more details.

## flashr2

This is a simple test [first try](flash_beta_test.html)

Initialization issue: [softimpute as initialization](missingimputeinitial.html)

Click here to find the [null check for flashr2](NULLcheck.html) and [densen nu case](nullcheck2.html)

### apply flashr2 for the examples in FLASH paper

@@

@@

>>>>

## Simulation studies

@@

### Apply flashr2 for the examples in FLASH paper

@@

Click here to check the [RMSE for the rank three example in the paper](simulation3.html) and [RRMSE](MSErank3sim.html)

@@

compare with PCA result[compare with SVD](PCAresult.html)
